MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-04-02 MAESTROeX_I/intro.tex
updates
added paragraph on recent low Mach papers

Previously, we developed the low Mach number astrophysical solver, MAESTRO.
The low Mach number model in MAESTRO is unique in that it is specifically designed for astrophysical settings with significant atmospheric stratification.
Central to the algorithm is a stratified background (or base) state density and pressure held in hydrostatic equilibrium, and also vary as a function of altitude and time.
MAESTRO is a structured-grid, finite-volume code that utlizes adaptive mesh refinement (AMR) to refine grids locally in space.
MAESTRO is suitable for for full spherical stars, as well as planar simulations of dynamics within localized regions of a star.

>>>>

In recent years, a number of alternative approaches to modelling low Mach number flows have been developed. These include semi-implicit all-Mach number solvers, where the Euler equations
are split into an acoustic part and an advective part \citep{Degond2009,Cordier2012,Haack2012,Chalons2016,Kwatra2009,Happenhofer2013,Padioleau2019}. The fast acoustic waves are then
solved using implicit time integration, while the slow material waves are solved explicitly. Another approach is to use preconditioned all-Mach number solvers
\citep{Miczek2014,Barsukow2016}, where the numerical flux is multiplied by a preconditioning matrix. This reduces the stiffness of the system at low Mach numbers, while retaining the
correct scaling behavior. In the reduced speed of sound technique (RSST) and related methods, the speed of sound is artificially reduced by including a suitable scaling factor in the
continuity equation, reducing the restriction on the size of the timestep \citep{Rempel2005,Hotta2012,Wang2015,Takeyama2017,Iijima2018}. The MUSIC code uses fully implicit time integration for the compressible Euler equations, which therefore allows for arbitrarily large timesteps \citep{Viallet2011,Viallet2015,Goffrey2016}.

Previously, we developed the low Mach number astrophysical solver, MAESTRO.
The low Mach number model in MAESTRO is unique in that it is specifically designed for astrophysical settings with significant atmospheric stratification.
Central to the algorithm is a stratified background (or base) state density and pressure held in hydrostatic equilibrium, and also vary as a function of altitude and time.
MAESTRO is a structured-grid, finite-volume code that utlizes adaptive mesh refinement (AMR) to refine grids locally in space.
This code was developed in the pure-Fortran90 FBoxLib framework (see the FBoxLib repository in \cite{AMReX}) for block-structured AMR applications.
MAESTRO is suitable for for full spherical stars, as well as planar simulations of dynamics within localized regions of a star.
